Algomusicology, ?, Profit

### 2016-04-02 paper.tex
Break the code up into sections.

\begin{verbatim}
(ns kolmogorov-music.talk
  (:require [clojure.repl :as repl]
            [midje.sweet :refer :all :exclude [after]]
            [overtone.live :refer :all :exclude [stop]]
            [leipzig.melody :refer :all]
            [leipzig.canon :as canon]
            [leipzig.scale :as scale]
            [leipzig.live :as live]
            [leipzig.live :refer [stop]]
            [leipzig.chord :as chord]
            [leipzig.temperament :as temperament]
            [kolmogorov-music.geb :as geb]
            [kolmogorov-music.coding :as coding]))

;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; Air on the \G String ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;

(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))

@@

;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; Analysis by compression ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;

(def row-row
  "A simple melody built from durations and pitches."
              ; Row, row, row  your boat,
  (->> (phrase [3/3  3/3  2/3  1/3  3/3]
               [  0    0    0    1    2])
       (then
                ; Gent-ly   down the  stream,
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  2    1    2    3    4]))
       (then    ; Merrily, merrily, merrily, merrily,
         (phrase (repeat 12 1/3)
                 (mapcat (partial repeat 3) [7 4 2 0])))
       (then
                ; Life is   but  a    dream!
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  4    3    2    1    0]))
       (canon/canon (canon/simple 4))
       (where :pitch (comp scale/A scale/major))))

@@

;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; The Library of Babel ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;

@@

;;;;;;;;;;;;;;;;
;;; Contact ;;;;
;;;;;;;;;;;;;;;;

@@

(fact "The Champernowne word is defined by concatenating the natural numbers base 10."
  (->> (champernowne-word) (take 16)) => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])

;;;;;;;;;;;;
;;; Anti ;;;
;;;;;;;;;;;;

>>>>

\section{Air on the \\G String}
\begin{verbatim}
(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))

@@

\section{Analysis by compression}

\begin{verbatim}
(def row-row
  "A simple melody built from durations and pitches."
              ; Row, row, row  your boat,
  (->> (phrase [3/3  3/3  2/3  1/3  3/3]
               [  0    0    0    1    2])
       (then
                ; Gent-ly   down the  stream,
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  2    1    2    3    4]))
       (then    ; Merrily, merrily, merrily, merrily,
         (phrase (repeat 12 1/3)
                 (mapcat (partial repeat 3) [7 4 2 0])))
       (then
                ; Life is   but  a    dream!
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  4    3    2    1    0]))
       (canon/canon (canon/simple 4))
       (where :pitch (comp scale/A scale/major))))

@@

\section{The Library of Babel}
\begin{verbatim}

@@

\section{Contact}
\begin{verbatim}

@@

(fact "The Champernowne word is defined by concatenating the natural numbers base 10."
  (->> (champernowne-word) (take 16)) => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
\end{verbatim}

\section{Anti}
\begin{verbatim}
